```{r, warning=FALSE, message=FALSE}
library("vtree")
library("dplyr")
```

# Source

<https://www.kaggle.com/datasets/piterfm/fifa-football-world-cup/data>

# License

<https://creativecommons.org/licenses/by-nc-sa/4.0/>

```{r}
fifa <- read.csv("matches_1930_2022.csv")
fifa <- fifa |> 
  mutate(
    HOME_OWN_GOAL = home_own_goal != "",
    AWAY_OWN_GOAL = away_own_goal != "",
    total_own_goals = HOME_OWN_GOAL + AWAY_OWN_GOAL,
    game = paste(home_team,"v",away_team,Year)
  )
```

home_team, away_team - Home and Away Teams,

home_score, away_score - Scores,

home_xg, away_xg - XG,

home_penalty, away_penalty- Penalties,

home_manager, away_manager - Managers,

home_captain, away_captain - Captains,

home_goal, away_goal - Scorers (Game),

home_goal_long, away_goal_long - Scorers (+Assistant),

home_own_goal, away_own_goal - Own Goal Scorers (OG),

home_penalty_goal, away_penalty_goal - Scorers (Penalty),

home_penalty_miss_long, away_penalty_miss_long - Miss Penalty (+Miss Reason),

home_penalty_shootout_miss_long, away_penalty_shootout_miss_long - Miss Penalty(After Game),

home_penalty_shootout_goal_long, away_penalty_shootout_goal_long- Penalty (After Game),

home_red_card, away_red_card - Red Cards (Direct),

home_yellow_red_card, away_yellow_red_card - Red Cards (Second Yellow),

home_yellow_card_long, away_yellow_card_long - Yellow Cards,

home_substitute_in_long, away_substitute_in_long - Substitutions,

Attendance,

Venue,

Officials,

Round,

Date,

Score,

Referee,

Notes,

Host,

Year,


```{r}
vtree(fifa, "HOME_OWN_GOAL AWAY_OWN_GOAL")
```


```{r}
vtree(fifa, "HOME_OWN_GOAL AWAY_OWN_GOAL", pattern = T)

```


What that one game was? 

```{r}
vtree(fifa, "HOME_OWN_GOAL AWAY_OWN_GOAL", 
      summary = "game \n%list%%var=AWAY_OWN_GOAL%%node=TRUE%")
```












